
\documentclass[aspectratio=169]{beamer}

\usepackage{booktabs}
\usepackage{array}
\usepackage{xcolor}

\definecolor{AccentPink}{HTML}{FF69B4}
\definecolor{AccentGreen}{HTML}{00AA44}

\setbeamertemplate{navigation symbols}{}
\setbeamercolor{background canvas}{bg=white}
\setbeamercolor{normal text}{fg=black,bg=white}

\title{\textbf{Jim's Data Gym}}
\subtitle{Training Analytical Judgment Through Deliberate Practice}
\author{James Donahue}
\date{}

\begin{document}

\begin{frame}[plain]
\titlepage
\vfill
{\small Practical skill development for the next generation of data professionals}
\end{frame}

\begin{frame}
\frametitle{\textcolor{AccentPink}{Problem \& Customer}}

\Large \textbf{Data Analysis Is Learned Through Practice, Not Content Consumption}

\vspace{0.4cm}

Traditional data science education excels at teaching tools, syntax, and theory. What it often fails to develop is the judgment required to work with messy, real-world data.

\begin{itemize}
\item Validating datasets and assumptions
\item Selecting appropriate methodologies
\item Interpreting ambiguous results
\item Making defensible analytical decisions
\end{itemize}

\textbf{Target Customers}
\begin{itemize}
\item Aspiring analysts seeking career progression
\item Career changers entering data-focused roles
\item SMEs looking to upskill existing talent rather than hire externally
\end{itemize}

\textcolor{AccentPink}{\textbf{The skills that matter most are rarely the skills being trained.}}
\end{frame}

\begin{frame}
\frametitle{\textcolor{AccentGreen}{Solution}}

\Large \textbf{Moving From Passive Learning to Deliberate Practice}

\vspace{0.3cm}

Jim's Data Gym transforms analytical skills into trainable micro-competencies.

\begin{columns}
\column{0.48\textwidth}
\textbf{Traditional Learning}
\begin{itemize}
\item Video lectures
\item Static tutorials
\item One-off projects
\item Limited repetition
\end{itemize}

\column{0.48\textwidth}
\textbf{Jim's Data Gym}
\begin{itemize}
\item Dynamic task generation
\item Structured practice loops
\item Progressive difficulty
\item Repeat until mastery
\end{itemize}
\end{columns}

\vspace{0.4cm}

Just as a physical gym isolates muscle groups, Jim's Data Gym isolates analytical skills including validation, reasoning, interpretation, and methodological decision-making.

\textcolor{AccentGreen}{\textbf{Building analytical muscle memory at scale.}}
\end{frame}

\begin{frame}
\frametitle{\textcolor{AccentPink}{Why Now}}

\Large \textbf{The Market Is Shifting Toward Judgment-Based Skills}

\vspace{0.3cm}

\textbf{Pedagogical Shift}

Modern language-learning platforms demonstrated that mastery comes from repeated active practice, not passive content consumption.

\vspace{0.2cm}

\textbf{Technology Shift}

As AI increasingly automates coding and implementation, human value moves toward framing problems, evaluating evidence, and making decisions.

\vspace{0.2cm}

\textbf{Market Opportunity}

Employers still struggle to identify candidates with practical analytical judgment despite an abundance of technical training resources.

\vspace{0.3cm}

\textcolor{AccentPink}{\textbf{AI can generate code. It cannot replace contextual judgment.}}
\end{frame}

\begin{frame}
\frametitle{\textcolor{AccentGreen}{Market \& Competition}}

\Large \textbf{Incumbents Optimize for Content. We Optimize for Competence.}

\vspace{0.3cm}

\small
\begin{tabular}{p{3.2cm} p{4.2cm} p{4.5cm}}
\toprule
\textbf{Category} & \textbf{Primary Limitation} & \textbf{Our Differentiation} \\
\midrule
Coursera / Udemy & Passive content consumption & Immediate hands-on execution \\
DataCamp / Dataquest & Guided syntax completion & Independent methodological reasoning \\
Kaggle / Bootcamps & Steep learning curve and overload & Structured micro-challenges with progression \\
\bottomrule
\end{tabular}

\vspace{0.5cm}

\textbf{Positioning}

Jim's Data Gym occupies the gap between learning concepts and performing confidently in professional environments.

\textcolor{AccentGreen}{\textbf{Less content. More capability.}}
\end{frame}

\begin{frame}
\frametitle{\textcolor{AccentPink}{Business Model \& Early Validation}}

\Large \textbf{Freemium Adoption, Institutional Expansion}

\vspace{0.3cm}

\textbf{Individual Users}
\begin{itemize}
\item Free core curriculum
\item Premium practice modules
\item AI-assisted feedback experiences
\end{itemize}

\textbf{Institutional Customers}
\begin{itemize}
\item Annual seat licenses
\item University departments
\item SMEs and research organizations
\item Custom datasets and instructor tools
\end{itemize}

\textbf{Validation Signals}
\begin{itemize}
\item Repeated interview feedback highlighting unmet demand
\item Active interest from academic and nonprofit stakeholders
\item Prospective users asking how to purchase today
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{\textcolor{AccentGreen}{Go-To-Market}}

\Large \textbf{Win Educators. Acquire Learners.}

\vspace{0.3cm}

\textbf{The Problem}

While educational content is abundant, instructors continue to spend significant time creating and maintaining practice exercises.

\vspace{0.2cm}

\textbf{Beachhead Strategy}

Provide free access and exercise-generation tools for professors, tutors, and training organizations.

\vspace{0.2cm}

\textbf{Current Momentum}

Discussions are underway with a local nonprofit regarding participation in a pilot initiative.

\vspace{0.2cm}

\textbf{Distribution Advantage}

Each instructor represents access to an entire cohort of highly engaged learners.

\vspace{0.3cm}

\textcolor{AccentGreen}{\textbf{Solve one educator's problem and reach hundreds of students.}}
\end{frame}

\begin{frame}
\frametitle{\textcolor{AccentPink}{Team}}

\Large \textbf{Domain Expertise + Education + Product Vision}

\vspace{0.4cm}

\textbf{James Donahue}

\begin{itemize}
\item Econometrician
\item English and German educator
\item EdTech builder
\item Data analytics practitioner
\item Specialist in adult learning and skill acquisition
\end{itemize}

\vspace{0.4cm}

\textbf{Why This Team}

A unique combination of analytical rigor, educational expertise, and deep understanding of how professionals develop practical skills.

\vfill

\textbf{Contact:} jimbodonahue@gmail.com
\end{frame}

\begin{frame}[plain]
\centering
\vfill
{\Huge \textbf{Thank You}}

\vspace{0.4cm}

{\Large Training the Next Generation of Data Thinkers}

\vfill
\textcolor{AccentPink}{www.jimsdatagym.com}
\end{frame}

\end{document}
